---
title: "Week 13"
author: "Raghu Chandramohan"
date: "`r format(Sys.Date(), format = '%d/%m/%Y')`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: kate
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
subtitle: Alcohol Consumption Around the World!
editor_options:
  chunk_output_type: console
---

### Load libraries

```{r}
library(fivethirtyeight)
library(tidyverse)
library(RColorBrewer)
```

### View the data
```{r}
drinks
glimpse(drinks)
```

###Download the lattitude and longitude for the world map.
There are some discrepancies between the countries listed in out 
```{r}
world_map_data = map_data(map = "world")
drinks$country[which(!(drinks$country %in% world_map_data$region))]
```

Swap out the mismatches
```{r}
countries_to_change = drinks$country
names(countries_to_change) = countries_to_change
countries_to_change[c("Antigua & Barbuda", "Bosnia-Herzegovina", "Cote d'Ivoire", "Cabo Verde", "Congo", "DR Congo", "Russian Federation", "United Kingdom")] = c("Antigua", "Bosnia and Herzegovina", "Ivory Coast", "Cape Verde", "Republic of Congo", "Democratic Republic of the Congo", "Russia", "UK")
drinks$country = unname(countries_to_change)

```

### Add new columns for total servings and preferred drink

```{r}
drinks_mod = drinks %>% arrange(desc(total_litres_of_pure_alcohol)) %>% mutate(total_servings = beer_servings + spirit_servings + wine_servings) %>% filter(total_servings > 10) %>% mutate(pref_drink = c("beer", "spirits", "wine")[max.col(.[2:4])])
```

### Plot world map and preferred drink
```{r}
right_join(drinks_mod, world_map_data, by = c('country' = 'region')) %>% 
  ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = group, fill = pref_drink), color = "white", size = 0.25) + 
  scale_fill_manual(values = c("#fecc5c", "#3690c0", "#d7191c"), na.value="#eff3ff") +
  guides(fill = guide_legend(keywidth = 6, keyheight = 1.5, title=NULL, label.position = "top", label.hjust = 0.5)) +
  labs(title= "Preferred drink around the world", subtitle = "countries which consume at least 10 servings per capita per year") + 
  theme(text=element_text(family="Verdana"),
        plot.title = element_text(hjust = 0.5, size=20), 
        plot.subtitle = element_text(hjust = 0.5, size = 12),
        legend.position = "top",
        legend.text=element_text(size=16),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.grid = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank()
        )

```


### Plot total pure alcohol consumption of top 15 countries and their preferred drink
```{r}
drinks_mod %>% 
  arrange(desc(total_litres_of_pure_alcohol)) %>% 
  top_n(15, total_litres_of_pure_alcohol) %>% 
  ggplot() +
  geom_bar( aes(x=reorder(country, total_litres_of_pure_alcohol), y=total_litres_of_pure_alcohol, fill=pref_drink), stat="identity", width=0.8) + 
  coord_flip() +
  scale_fill_manual(values = c("#fecc5c", "#3690c0", "#d7191c"), na.value="#eff3ff") +
  guides(fill = guide_legend(keywidth = 6, keyheight = 1.5, title=NULL, label.position = "top", label.hjust = 0.5)) +
    labs(title= "Top 15 countries with maximum alcohol consumption and their preferred drink type") + 
  ylab(label = "Total litres of pure alcohol consumed") + 
  xlab(label = "Countries") +
  theme(text=element_text(family="Verdana"),
        plot.title = element_text(hjust = 0.5, size=20), 
        plot.subtitle = element_text(hjust = 0.5, size = 16),
        legend.position = "top",
        legend.text=element_text(size=16),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.grid = element_blank()
        )

```

Original work by Veerle van Son. This work was mimiced purely for learning purposes.